---
title: "figs_tabs_results"
output:
  word_document: default
  pdf_document: default
---

```{r import, echo=FALSE}
#Possible palettes #1: #538797, #C2D9CD, #FF842A https://www.instagram.com/p/B9En6h2gbJ5/
#Possible palette #2: #238189, #3FA8B3, #E8F3EE, #FF674D https://www.instagram.com/p/BxZZu82gBm3/
#File structure
rootdir <- rprojroot::find_root(rprojroot::has_dir("src"))
srcdir <- file.path(rootdir, 'src', 'globalIRmap_anthropo')
datdir <- file.path(rootdir, 'data')
resdir <- file.path(rootdir, 'results')

#Source packages functions
library(drake)
library(flextable)
library(grid)
source(file.path(srcdir, 'R/IRmapping_packages.R'))
source(file.path(srcdir, 'R/IRmapping_functions.R'))
source(file.path(srcdir, 'R/IRmapping_plan.R'))

loadd(gpredsdt)
loadd(rivpred)
loadd(tasks_u10)
loadd(tasks_featsel_u10)
loadd(tasks_featsel_o1)
```


#Geographical distribution of reference streamgauging stations
##Statistics for paper
- Number of gauges in total: \         
`r gpredsdt[, .N]` \
- Number of perennial gauges used in analysis (average number of years of data): \
`r gpredsdt[intermittent_o1800==0, .N]`(`r gpredsdt[intermittent_o1800==0, mean(totalYears_kept_o1800)]`) \
- Number of intermittent gauges taking in account only post-1800, mDur >= 1 (average number of years of data): \
`r gpredsdt[intermittent_o1800==1, .N]`(`r gpredsdt[intermittent_o1800==1, mean(totalYears_kept_o1800)]`) \
- Number of intermittent gauges taking in account only post-1800, mDur > 0 (average number of years of data): \
`r gpredsdt[mDur_o1800>0, .N]` \
- Number of intermittent gauges taking in account only post-1800, mDur >= 30 (average number of years of data): \
`r gpredsdt[mDur_o1800>=30, .N]` \
- Number of reaches in network: \
`r rivpred[disan_m3_pyr > 0.1 & INLAKEPERC < 1, .N]` \
- Average length of reaches in network: \
`r rivpred[disan_m3_pyr > 0.1 & INLAKEPERC < 1, mean(LENGTH_KM*(1-INLAKEPERC))]` \
- Total length of reaches in network: \
`r rivpred[disan_m3_pyr > 0.1 & INLAKEPERC < 1, sum(LENGTH_KM*(1-INLAKEPERC))]` \
- Total number of predictor variables: \
`r length(tasks_u10$classif$feature_names)` \
- Total number of predictor variables kept in model for gauges < 10 m3/s: \
`r length(tasks_featsel_u10[[2]]$feature_names)` \
- Total number of predictor variables kept in model for gauges >= 1 m3/s: \
`r length(tasks_featsel_o1[[2]]$feature_names)` \


```{r clean-targets, echo=FALSE}
remove(gpredsdt)
remove(rivpred)
remove(tasks_u10)
remove(tasks_featsel_u10)
remove(tasks_featsel_o1)
gc()
```

#Threshold sensitivity
```{r threshold-sensitivity, fig.height = 6, fig.height = 6, dpi=600, echo = FALSE}
loadd(threshold_sensitivity)

png(paste0(file.path(resdir, 'figures//thresholdsensitivty_anthropo'), 
           format(Sys.Date(), '%Y%m%d'), '.png'), 
    width=6, height=6, units='in', res=600)
print(threshold_sensitivity$gperf)
dev.off()

print(threshold_sensitivity$predbounds)
```

#Methods - Table 2. Specification and benchmark comparison of models
```{r models-benchmarking-table, echo=FALSE}
loadd(tablebm_classif1_u10)
loadd(tablebm_classif2_u10)
print('Setup table u10')
setup_table_u10 <- rbindlist(list(tablebm_classif1_u10$setup,
                              tablebm_classif2_u10$setup),
                         fill=T, use.names=T)

flextable(setup_table_u10)

print('Results table u10')
results_table_u10 <- rbindlist(list(tablebm_classif1_u10$results,
                                tablebm_classif2_u10$results),
                           fill=T, use.names=T)
flextable(results_table_u10)

print('Setup table o1')
loadd(tablebm_classif1_o1)
loadd(tablebm_classif2_o1)
setup_table_o1 <- rbindlist(list(tablebm_classif1_o1$setup,
                              tablebm_classif2_o1$setup),
                         fill=T, use.names=T)

flextable(setup_table_o1)

print('Results table o1')
results_table_o1 <- rbindlist(list(tablebm_classif1_o1$results,
                              tablebm_classif2_o1$results),
                         fill=T, use.names=T)
flextable(results_table_o1)

remove(tablebm_classif1_u10)
remove(tablebm_classif2_u10)
gc()
```


#Main text - Figure 2. Variable importance for top 20 variables
```{r variable-importance, fig.width=7.5, fig.height=6, dpi=600, echo=FALSE}
loadd(vimp_plot_u10)
loadd(vimp_plot_o1)

fwrite(vimp_plot_u10$data[, .(varnames, imp_wmean, imp_wsd, Keyscale, Keystat, 
                              Category, Attribute, Source, Citation, varname)],
       paste0(file.path(resdir, 'figures//vimpdata_u10_anthropo_'), 
           format(Sys.Date(), '%Y%m%d'), '.csv')
)

fwrite(vimp_plot_o1$data[, .(varnames, imp_wmean, imp_wsd, Keyscale, Keystat, 
                              Category, Attribute, Source, Citation, varname)],
       paste0(file.path(resdir, 'figures//vimpdata_o1_anthropo_'), 
           format(Sys.Date(), '%Y%m%d'), '.csv')
)

p_u10 <- vimp_plot_u10 +
  theme(plot.margin = unit(c(10,260,0,0), "pt")) +
  labs(x=bquote('A. Gauges with mean annual discharge < 10'~m^3~s^-1)) + 
  theme(plot.margin = unit(c(0,0,0,0), 'cm'))

p_o1format <- vimp_plot_o1 +
  coord_flip(ylim=c(min(vimp_plot_o1$data[, max(imp_wmean+imp_wsd)+1], 100), 0),
             clip='off') +
  scale_x_discrete(name=expression(
    B.~Gauges~with~mean~annual~discharge >= 1~m^3~s^-1),
    labels = function(x) {
      stringr::str_wrap(tolower(x), width = 25)
    },
    limits = rev,
    position='top') +
  scale_y_reverse(position='right', expand=c(0,0)) +
  theme(legend.position = 'none',
        plot.background = element_blank(),
        panel.background = element_blank(),
        plot.margin = unit(c(0,0,0,0.1), 'cm'))

pdf(paste0(file.path(resdir, 'figures//vimp_anthropo_'), 
           format(Sys.Date(), '%Y%m%d'), '.pdf'), 
    width=7.5, height=6)
p_u10 + p_o1format
dev.off()

remove(vimp_plot_u10)
remove(vimp_plot_o1)
gc()
```

#Main text - Figure 3. Partial dependence plots
```{r partial-dependence, fig.width=12, fig.height=12, echo=FALSE}
loadd(pd_plot_u10)
lapply(pd_plot_u10, function(p) plot(p))

loadd(pd_plot_o1)
lapply(pd_plot_o1, function(p) plot(p))

remove(pd_plot_u10)
remove(pd_plot_o1)
gc()
```

#Final binned summary statistics for split model approach(< 10 and >= 1)
```{r binned_misclas, echo=FALSE}
loadd(bin_finalmisclass_IRpredcat_CVnosp)
loadd(bin_finalmisclass_IRpredcat_CVsp)
loadd(gpredsdt)

print('Split model approach: 3-fold non-spatial CV')
print(paste0(
  'Overal bacc:', 
  gpredsdt[, round(mlr3measures::bacc(intermittent_o1800, 
                                      as.factor(IRpredcat_CVnosp)),
                   2)]
)
)
flextable(bin_finalmisclass_IRpredcat_CVnosp)

print('Slit model approach: 40-fold spatial CV')
print(paste0(
  'Overal bacc:', 
  gpredsdt[, round(mlr3measures::bacc(intermittent_o1800, 
                                      as.factor(IRpredcat_CVsp)),
                   2)]
)
)
flextable(bin_finalmisclass_IRpredcat_CVsp)

remove(bin_finalmisclass_IRpredcat_CVnosp)
remove(bin_finalmisclass_IRpredcat_CVsp)
```

#Statistics and figure for AFI across network
```{r afi-net, echo=FALSE}
loadd(netchange)
print(netchange$stat)

pdf(paste0(file.path(resdir, 'figures//netIRanthropo_barplot'), 
           format(Sys.Date(), '%Y%m%d'), '.pdf'), 
    width=7.5, height=6)
netchange$plot
dev.off()

```



#Environmental variables used in model training  + variable selection results
```{r variabl-figure, echo=FALSE}
loadd(predvars)

#Write predvars to csv
fwrite(predvars, file.path(resdir, paste0('predictor_variables_anthropo.csv')))

#Make table
flextable(predvars[,c('Category', 'Attribute', 'Spatial representation',
                      'Temporal/Statistical aggreg.', 'Source', 'Citation'),
                   with=F])

remove(predvars)
gc()
```

#Tables of intermittence by categories for base model
```{r inter-tables, echo=FALSE}

tablist <- list('', 'climatetable_notanthropo',
                    'basintable_anthropo', 'basintable_anthropo')

format_summarytab <- function(tab) {
  numcols <- names(tab)[tab[,sapply(.SD, class)=='numeric']]
  out_tab <- flextable(tab[, (numcols) := lapply(.SD, function(x) as.integer(round(x))),
                           .SDcols = numcols]) %>%
    autofit
  return(out_tab)
}


print('climate_anthropo')
format_summarytab(drake::readd(climatetable_anthropo)$'0.5')

print('climate_notanthropo')
format_summarytab(drake::readd(climatetable_notanthropo)$'0.5')

print('basin_anthropo')
format_summarytab(drake::readd(basintable_anthropo)$'0.5')

print('basin_notanthropo')
format_summarytab(drake::readd(basintable_notanthropo)$'0.5')
```
